Student Log-Data from a Randomized Evaluation of Educational Technology: A Causal Case Study

### 2020-02-10 paper.Rnw
small edit to sec 6

\section{Comparing Strategies}\label{sec:synthesis}
The goals, assumptions, and processes of matching, mediation analysis,
and principal stratification, when applied to implementation data from
an EdTech RCT, each differ from each other, but also overlap in
interesting ways.
In the case discussed here, the observational study and mediation
approaches appear to give the opposite conclusion from principal
stratification.
This section will compare and contrast the three methods in terms of
 their necessary identification assumptions, their model fitting
 mechanics, and interpretation of their results.

>>>>

\section{Comparing Strategies}\label{sec:synthesis}
The goals, assumptions, and processes of matching, mediation analysis,
and principal stratification, when applied to implementation data from
an EdTech RCT, each differ from each other, but also overlap in
interesting ways.
In the case discussed here, the observational study and mediation
approaches appear to give the opposite conclusion from principal
stratification---matching and mediation suggest that exessive hint
requests hurt students' posttest scores, while principal
stratification suggests that students who request more hints
experiance higher treatment effects.
This section will compare and contrast the three methods in terms of
 their necessary identification assumptions, their model fitting
 mechanics, and interpretation of their results.
